MINOS Handover Plots

### 2024-02-26 minos/validation/handovers.Rmd

## Net Income & Rent & Mortgage

```{r yearly_energy}
# get required variables. 
raw.inc <- raw.dat %>%
  select(pidp, age, time, net_hh_income, hh_rent, hh_mortgage, council_tax, oecd_equiv)
base.inc <- base.dat %>%
  select(pidp, age, time, net_hh_income, hh_rent, hh_mortgage, council_tax, oecd_equiv)

# net household income. 
handover_boxplots(raw.inc, base.inc, 'net_hh_income')
handover_lineplots(raw.inc, base.inc, "net_hh_income")
inc.spag<-rbind(raw.inc, base.inc)
density_ridges(inc.spag, 'net_hh_income',
               save=TRUE, 
               save.path=save.path)

# rent
handover_boxplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], 'hh_rent')
handover_lineplots(raw.inc[which(raw.inc$hh_rent>1), ], base.inc[which(base.inc$hh_rent>1), ], "hh_rent")
density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
               save=TRUE, 
               save.path=save.path)

# mortgage
handover_boxplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], 'hh_mortgage')
handover_lineplots(raw.inc[which(raw.inc$hh_mortgage>1), ], base.inc[which(base.inc$hh_mortgage>1), ], "hh_mortgage")
density_ridges(inc.spag[which(inc.spag$hh_mortgage>1), ], 'hh_mortgage',
               save=TRUE, 
               save.path=save.path)

#council tax
handover_boxplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], 'council_tax')
handover_lineplots(raw.inc[which(raw.inc$council_tax>1), ], base.inc[which(base.inc$council_tax>1), ], "council_tax")
density_ridges(inc.spag[which(inc.spag$council_tax>1), ], 'council_tax',
               save=TRUE, 
               save.path=save.path)

# oecd equivalence scale. (NOT TRANSITIONED YET. REQUIRES LEAVING THE NEST MODULE.. )
handover_boxplots(raw.inc, base.inc, 'oecd_equiv')
handover_lineplots(raw.inc, base.inc, 'oecd_equiv')
density_ridges(inc.spag, 'oecd_equiv',
               save=TRUE, 
               save.path=save.path)

# tidy up.
rm(raw.inc, base.inc, inc.spag)
```

## Yearly energy

```{r net_income}
# get required variables. 
raw.energy <- raw.dat %>%
  select(pidp, age, time, yearly_energy, yearly_gas, yearly_electric)
base.energy <- base.dat %>%
  select(pidp, age, time, yearly_energy, yearly_gas, yearly_electric)

# gas expenditure
handover_boxplots(raw.energy, base.energy, 'yearly_gas')
handover_lineplots(raw.energy, base.energy, "yearly_gas")
#inc.spag<-rbind(raw.inc, base.inc)
#density_ridges(inc.spag, 'yearly_gas',
#               save=TRUE, 
#               save.path=save.path)

# yearly electric
handover_boxplots(raw.energy, base.energy, 'yearly_electric')
handover_lineplots(raw.energy, base.energy, "yearly_electric")
#density_ridges(inc.spag[which(inc.spag$hh_rent>1), ], 'hh_rent',
#               save=TRUE, 
#               save.path=save.path)

# yearly energy
handover_boxplots(raw.energy, base.energy, 'yearly_energy')
handover_lineplots(raw.energy, base.energy, "yearly_energy")
#density_ridges(inc.spag[which(inc.spag$hh_mortgage>1), ], 'hh_mortgage',
#               save=TRUE, 
#               save.path=save.path)

# tidy up.
rm(raw.energy, base.energy)#, inc.spag)
```

@@

```{r}
raw.child.ages <- raw.dat %>%
  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
  filter(time > 2013) %>%
  group_by(time, hidp) %>%
  summarise(child_ages = find_mode(child_ages))

>>>>

@@

```{r}
raw.child.ages <- raw.dat %>%
  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
  filter(time > 2013 & child_ages != 'childless') %>%
  group_by(time, hidp) %>%
  summarise(child_ages = find_mode(child_ages))
